P versus NP

### 2020-02-25 doc/manuscript.tex
Changed the title
We update the content proof.

%\titlerunning{P vs NP}%optional, please use if title is longer than one line

@@

\keywords{complexity classes, completeness, polynomial time, reduction, logarithmic space}%TODO mandatory; please add comma-separated list of keywords

@@

%TODO mandatory: add short abstract of the document
\begin{abstract}
P versus NP is considered as one of the most important open problems in computer science. This consists in knowing the answer of the following question: Is P equal to NP? It was essentially mentioned in 1955 from a letter written by John Nash to the United States National Security Agency. However, a precise statement of the P versus NP problem was introduced independently by Stephen Cook and Leonid Levin. Since that date, all efforts to find a proof for this problem have failed. Another major complexity classes are L and NL. Whether L = NL is another fundamental question that it is as important as it is unresolved. We demonstrate if L is not equal to NL, then P = NP. In addition, we show if L is equal to NL, then P = NP. In this way, we prove the complexity class P is equal to NP. Furthermore, we demonstrate the complexity class NL is equal to NP.
\end{abstract}

@@

Let $\Sigma$ be a finite alphabet with at least two elements, and let $\Sigma^{*}$ be the set of finite strings over $\Sigma$ \cite{AB09}. A Turing machine $M$ has an associated input alphabet $\Sigma$ \cite{AB09}. For each string $w$ in $\Sigma^{*}$ there is a computation associated with $M$ on input $w$ \cite{AB09}. We say that $M$ accepts $w$ if this computation terminates in the accepting state, that is $M(w)=1$ \cite{AB09}. Note that $M$ fails to accept $w$ either if this computation ends in the rejecting state, that is $M(w)=0$, or if the computation fails to terminate, or the computation ends in the halting state with some output, that is $M(w)=y$ (when $M$ outputs the string $y$ on the input $w$) \cite{AB09}.

Another relevant advance in the last century has been the definition of a complexity class. A language over an alphabet is any set of strings made up of symbols from that alphabet \cite{CLRS01}. A complexity class is a set of problems, which are represented as a language, grouped by measures such as the running time, memory, etc \cite{CLRS01}. The language accepted by a Turing machine $M$, denoted $L(M)$, has an associated alphabet $\Sigma$ and is defined by:
\[L(M) = \{w \in \Sigma^{*}: M(w)=1 \}.\]
Moreover, $L(M)$ is decided by $M$, when $w \notin L(M)$ if and only if $M(w)=0$ \cite{CLRS01}. We denote by $t_{M}(w)$ the number of steps in the computation of $M$ on input $w$ \cite{AB09}. For $n \in \mathbb{N}$ we denote by $T_{M}(n)$ the worst case run time of $M$; that is:
\[T_{M}(n) = max\{t_{M}(w): w \in \Sigma^{n} \}\]
where $\Sigma^{n}$ is the set of all strings over $\Sigma$ of length $n$ \cite{AB09}. We say that $M$ runs in polynomial time if there is a constant $k$ such that for all $n$, $T_{M}(n) \leq n^{k} + k$ \cite{AB09}. In other words, this means the language $L(M)$ can be decided by the Turing machine $M$ in polynomial time. Therefore, $P$ is the complexity class of languages that can be decided by deterministic Turing machines in polynomial time \cite{CLRS01}. A verifier for a language $L_{1}$ is a deterministic Turing machine $M$, where:
\[L_{1} = \{w: M(w, c) = 1 \textit{ for some string } c\}.\]
We measure the time of a verifier only in terms of the length of $w$, so a polynomial time verifier runs in polynomial time in the length of $w$ \cite{AB09}. A verifier uses additional information, represented by the symbol $c$, to verify that a string $w$ is a member of $L_{1}$. This information is called certificate. $NP$ is the complexity class of languages defined by polynomial time verifiers \cite{Pap03}.

@@

A logarithmic space transducer is a Turing machine with a read-only input tape, a write-only output tape, and read/write work tapes \cite{MS06}. The work tapes must contain at most $O(\log n)$ symbols \cite{MS06}. A logarithmic space transducer $M$ computes a function $f : \Sigma^{*} \rightarrow \Sigma^{*}$, where $f(w)$ is the string remaining on the output tape after $M$ halts when it is started with $w$ on its input tape \cite{MS06}. We call $f$ a logarithmic space computable function \cite{MS06}. We say that a language $L_{1} \subseteq \{0, 1\}^{*}$ is logarithmic space reducible to a language $L_{2} \subseteq \{0, 1\}^{*}$, written $L_{1} \leq_{l} L_{2}$, if there exists a logarithmic space computable function $f : \{0, 1\}^{*} \rightarrow \{0, 1\}^{*}$ such that for all $x \in \{0, 1\}^{*}$:
\[x \in L_{1} \textit{ if and only if } f(x) \in L_{2}.\]
The logarithmic space reduction is used in the definition of the complete languages for the classes $L$ and $NL$ \cite{Pap03}. A Boolean formula is in 2-conjunctive normal form, or $2CNF$, if it is in $CNF$ and each clause has exactly two distinct literals. There is a problem called $2SAT$, where we asked whether a given Boolean formula $\phi$ in $2CNF$ is satisfiable. $2SAT$ is complete for $NL$ \cite{Pap03}. Another special case is the class of problems where each clause contains $XOR$ (i.e. exclusive or) rather than (plain) $OR$ operators. This is in $P$, since an $\textit{XOR SAT}$ formula can also be viewed as a system of linear equations mod $2$, and can be solved in cubic time by Gaussian elimination \cite{MM11}. We denote the $XOR$ function as $\oplus$. The $\textit{XOR 2SAT}$ problem will be equivalent to $\textit{XOR SAT}$, but the clauses in the formula have exactly two distinct literals. $\textit{XOR 2SAT}$ is in $L$ \cite{AR00}, \cite{RM08}.

@@

\begin{definition}
A language $L_{1}$ is in $NL$ if there exists a deterministic logarithmic space Turing machine $M$ with an additional special read-once input tape polynomial $p: \mathbb{N} \rightarrow \mathbb{N}$ such that for every $x \in \{0, 1\}^{*}$:
\[x \in L_{1} \Leftrightarrow \exists \textit{ appropriated } u \in \{0, 1\}^{p(|x|)} \textit{ such that } M(x, u) = 1 \]
where by $M(x, u)$ we denote the computation of $M$ where $x$ is placed on its input tape and the certificate $u$ is placed on its special read-once tape, and $M$ uses at most $O(\log |x|)$ space on its read/write tapes for every input $x$ where $|\ldots|$ is the bit-length function \cite{AB09}. $M$ is called a logarithmic space verifier \cite{AB09}.
\end{definition}

@@

\begin{hypothesis}
\label{hypothesis1}
Given a nonempty language $L_{1} \in L$, there is a language $L_{2}$ in $\textit{NP--complete}$ with a deterministic Turing machine $M$, where:
\[L_{2} = \{w: M(w, u) = y, \exists \textit{ appropriated } u \textit{ such that } y \in L_{1}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$. In this way, there is an $\textit{NP--complete}$ language defined by a logarithmic space verifier $M$ such that when the input is an element of the language with its certificate, then $M$ outputs a string which belongs to a single language in $L$.
\end{hypothesis}

\begin{theorem}
\label{implication}
When the Hypothesis \ref{hypothesis1} is true, therefore if $L_{2}$ is $\textit{NP--complete}$ under logarithmic space reduction, then $NL = NP$.
\end{theorem}

\begin{proof}
Since every problem in $L$ is $\textit{L--complete}$ under logarithmic space reduction, then we can interpret the quantification of the above statement as $``$For any nonempty language $L_{1}$ in $L$, there is an $\textit{NP--complete}$ language $L_{2}$ $\ldots$ (rest is the same)$"$. However, if we can choose an arbitrary language $L_{1}$ in $L$, then choosing $L_{1}$ the trivial language $\{1\}$ will result in the right hand side of the expression defining $L_{2}$ contained in $NL$. Moreover, if that problem in $NL$ is $\textit{NP--complete}$ under logarithmic space reduction, then we obtain that certainly $NL = NP$.
\end{proof}

@@

We show a previous known $\textit{NP--complete}$ problem:

\begin{definition}
$\textbf{NAE 3SAT}$

@@

QUESTION: Is there a truth assignment for $\phi$ such that each clause has at least one true literal and at least one false literal?

REMARKS: $\textit{NAE 3SAT} \in \textit{NP--complete}$ \cite{GJ79}.
\end{definition}

@@

\begin{definition}
$\textbf{MAXIMUM EXCLUSIVE-OR 2SAT}$

INSTANCE: A positive integer $K$ and a Boolean formula $\phi$ that is an instance of $\textit{XOR 2SAT}$.

QUESTION: Is there a truth assignment in $\phi$ such that at most $K$ clauses are unsatisfied?

REMARKS: We denote this problem as $MAX\oplus2SAT$.
\end{definition}

\begin{theorem}
\label{completeness}
$MAX\oplus2SAT \in \textit{NP--complete}$.
\end{theorem}

\begin{proof}
It is trivial to see $MAX\oplus2SAT \in NP$ \cite{Pap03}. Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses, we create three new variables $a_{c_{i}}$, $b_{c_{i}}$ and $d_{c_{i}}$ for each clause $c_{i} = (x \vee y \vee z)$ in $\phi$, where $x$, $y$ and $z$ are literals, in the following formula:
\[P_{i} = (a_{c_{i}} \oplus b_{c_{i}}) \wedge (b_{c_{i}} \oplus d_{c_{i}}) \wedge (a_{c_{i}} \oplus d_{c_{i}}) \wedge (x \oplus a_{c_{i}}) \wedge (y \oplus b_{c_{i}}) \wedge (z \oplus d_{c_{i}}).\]
We can see $P_{i}$ has at most one unsatisfied clause for some truth assignment if and only if at least one member of $\{x,y,z\}$ is true and at least one member of $\{x,y,z\}$ is false for the same truth assignment. Hence, we can create the Boolean formula $\psi$ as the conjunction of the $P_{i}$ formulas for every clause $c_{i}$ in $\phi$, such that $\psi = P_{1} \wedge \ldots \wedge P_{m}$. Finally, we obtain that:
\[\phi \in \textit{NAE 3SAT} \textit{ if and only if } (\psi, m) \in MAX\oplus2SAT.\]
Consequently, we prove $\textit{NAE 3SAT} \leq_{p} MAX\oplus2SAT$ where we already know the language $\textit{NAE 3SAT} \in \textit{NP--complete}$ \cite{GJ79}. To sum up, we show $MAX\oplus2SAT \in \textit{NP--hard}$ and $MAX\oplus2SAT \in NP$ and thus, $MAX\oplus2SAT \in \textit{NP--complete}$.
\end{proof}

\begin{theorem}
\label{proof}
There is a deterministic Turing machine $M$, where:
\[MAX\oplus2SAT = \{w: M(w, u) = y, \exists \textit{ appropriated } u \textit{ such that } y \in \textit{XOR 2SAT}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
\end{theorem}

\begin{proof}
Given a valid instance $(\psi, K)$ for $MAX\oplus2SAT$ when $\psi$ has $m$ clauses, we can create a certificate array $A$ which contains $K$ different natural numbers in ascending order which represents the indexes of the clauses in $\psi$ that we are going to remove from the instance. We read at once the elements of the array $A$ and we reject whether this is not an appropriated certificate: That is when the numbers are not sorted in ascending order, or the array $A$ does not contain exactly $K$ elements, or the array $A$ contains a number that is not between $1$ and $m$. While we read the elements of the array $A$, we remove the clauses from the instance $(\psi, K)$ for $MAX\oplus2SAT$ just creating another instance $\phi$ for $\textit{XOR 2SAT}$ where the Boolean formula $\phi$ does not contain the $K$ different indexed clauses $\psi$ represented by the numbers in $A$. Therefore, we obtain the array $A$ would be valid according to the Theorem \ref{proof} when:
\[(\psi, K) \in MAX\oplus2SAT \Leftrightarrow (\exists \textit{ appropriated array } A \textit{ such that } \phi \in \textit{XOR 2SAT}).\]
Furthermore, we can make this verification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$ and we assume the clauses in the input $\psi$ are indexed from left to right. Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated certificate and also remove the $K$ different clauses from the Boolean formula $\psi$ when we write the final clauses to the output. This logarithmic space verification will be the Algorithm \ref{algorithm1}. We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = \textit{undefined}$. In addition, we reject immediately when the following comparisons:
\[A[i] \leq max \vee A[i] < 1 \vee A[i] > m\]
hold at least into one single binary digit. Note, in the loop $j$ from $min$ to $max - 1$, we do not output any clause when $max - 1 < min$.

\begin{algorithm}
\caption{Logarithmic space verifier}\label{algorithm1}
\begin{algorithmic}[1]
\Comment{A valid instance for $MAX\oplus2SAT$ with its certificate}
\Procedure{$\textit{VERIFIER}$}{$(\psi, K), A$}
\Comment{Initialize minimum and maximum values}
\State $min \gets 1$
\State $max \gets 0$
\Comment{Iterate for the elements of the certificate array $A$}
\For{$i$}{$1$}{$K + 1$}
\If{$i = K+1$}
\Comment{There exists a $K+1$ element in the array}
\If{$A[i] \neq \textit{undefined}$}
\Comment{Reject the certificate}
\State \textbf{return} $0$
\EndIf
\Comment{$m$ is the number of clauses in $\psi$}
\State $max \gets m + 1$
\ElsIf{$A[i] = \textit{undefined} \vee A[i] \leq max \vee A[i] < 1 \vee A[i] > m$}
\Comment{Reject the certificate}
\State \textbf{return} $0$
\Else
\State $max \gets A[i]$
\EndIf
\Comment{Iterate for the clauses of the Boolean formula $\psi$}
\For{$j$}{$min$}{$max - 1$}
\Comment{Output the indexed $j^{th}$ clause in $\psi$}
\State \textbf{output} $``\wedge c_{j}"$
\EndFor
\State $min \gets max + 1$
\EndFor
\EndProcedure
\end{algorithmic}
\end{algorithm}
\end{proof}

\begin{theorem}
\label{result1}
The Hypothesis \ref{hypothesis1} is true.
\end{theorem}

\begin{proof}
This is a consequence of Theorems \ref{completeness} and \ref{proof}.
\end{proof}

\begin{theorem}
\label{nl}
$NL = NP$ and thus, $P = NP$.
\end{theorem}

>>>>

\titlerunning{P vs NP}%optional, please use if title is longer than one line

@@

\keywords{complexity classes, completeness, polynomial time, reduction, logarithmic space, one-way}%TODO mandatory; please add comma-separated list of keywords

@@

%TODO mandatory: add short abstract of the document
\begin{abstract}
P versus NP is considered as one of the most important open problems in computer science. This consists in knowing the answer of the following question: Is P equal to NP? It was essentially mentioned in 1955 from a letter written by John Nash to the United States National Security Agency. However, a precise statement of the P versus NP problem was introduced independently by Stephen Cook and Leonid Levin. Since that date, all efforts to find a proof for this problem have failed. Another major complexity classes are L and NL. Whether L = NL is another fundamental question that it is as important as it is unresolved. We show if L is equal to NL, then P = NP. In addition, we demonstrate that L is equal to NL. In this way, we prove the complexity class P is equal to NP.
\end{abstract}

@@

Let $\Sigma$ be a finite alphabet with at least two elements, and let $\Sigma^{*}$ be the set of finite strings over $\Sigma$ \cite{AB09}. A Turing machine $M$ has an associated input alphabet $\Sigma$ \cite{AB09}. For each string $w$ in $\Sigma^{*}$ there is a computation associated with $M$ on input $w$ \cite{AB09}. We say that $M$ accepts $w$ if this computation terminates in the accepting state, that is $M(w)=``yes"$ \cite{AB09}. Note that $M$ fails to accept $w$ either if this computation ends in the rejecting state, that is $M(w)=``no"$, or if the computation fails to terminate, or the computation ends in the halting state with some output, that is $M(w)=y$ (when $M$ outputs the string $y$ on the input $w$) \cite{AB09}.

Another relevant advance in the last century has been the definition of a complexity class. A language over an alphabet is any set of strings made up of symbols from that alphabet \cite{CLRS01}. A complexity class is a set of problems, which are represented as a language, grouped by measures such as the running time, memory, etc \cite{CLRS01}. The language accepted by a Turing machine $M$, denoted $L(M)$, has an associated alphabet $\Sigma$ and is defined by:
\[L(M) = \{w \in \Sigma^{*}: M(w)=``yes" \}.\]
Moreover, $L(M)$ is decided by $M$, when $w \notin L(M)$ if and only if $M(w)=``no"$ \cite{CLRS01}. We denote by $t_{M}(w)$ the number of steps in the computation of $M$ on input $w$ \cite{AB09}. For $n \in \mathbb{N}$ we denote by $T_{M}(n)$ the worst case run time of $M$; that is:
\[T_{M}(n) = max\{t_{M}(w): w \in \Sigma^{n} \}\]
where $\Sigma^{n}$ is the set of all strings over $\Sigma$ of length $n$ \cite{AB09}. We say that $M$ runs in polynomial time if there is a constant $k$ such that for all $n$, $T_{M}(n) \leq n^{k} + k$ \cite{AB09}. In other words, this means the language $L(M)$ can be decided by the Turing machine $M$ in polynomial time. Therefore, $P$ is the complexity class of languages that can be decided by deterministic Turing machines in polynomial time \cite{CLRS01}. A verifier for a language $L_{1}$ is a deterministic Turing machine $M$, where:
\[L_{1} = \{w: M(w, c) = ``yes" \textit{ for some string } c\}.\]
We measure the time of a verifier only in terms of the length of $w$, so a polynomial time verifier runs in polynomial time in the length of $w$ \cite{AB09}. A verifier uses additional information, represented by the symbol $c$, to verify that a string $w$ is a member of $L_{1}$. This information is called certificate. $NP$ is the complexity class of languages defined by polynomial time verifiers \cite{Pap03}. If $NP$ is the class of problems that have succinct certificates, then the complexity class $coNP$ must contain those problems that have succinct disqualifications \cite{Pap03}. That is, a $``no"$ instance of a problem in $coNP$ possesses a short proof of its being a $``no"$ instance \cite{Pap03}.

\begin{definition}
We will extend the definition of succinct disqualification for an element $w \in L_{2}$ when $L_{2} \in coNP$ as the polynomially bounded string $c$ by $w$ such that $M(w, c) = ``no"$ and $M$ is the polynomial time verifier of the complement of $L_{2}$ in $NP$.
\end{definition}

@@

A logarithmic space transducer is a Turing machine with a read-only input tape, a write-only output tape, and read/write work tapes \cite{MS06}. The work tapes must contain at most $O(\log n)$ symbols \cite{MS06}. A logarithmic space transducer $M$ computes a function $f : \Sigma^{*} \rightarrow \Sigma^{*}$, where $f(w)$ is the string remaining on the output tape after $M$ halts when it is started with $w$ on its input tape \cite{MS06}. We call $f$ a logarithmic space computable function \cite{MS06}. We say that a language $L_{1} \subseteq \{0, 1\}^{*}$ is logarithmic space reducible to a language $L_{2} \subseteq \{0, 1\}^{*}$, written $L_{1} \leq_{l} L_{2}$, if there exists a logarithmic space computable function $f : \{0, 1\}^{*} \rightarrow \{0, 1\}^{*}$ such that for all $x \in \{0, 1\}^{*}$:
\[x \in L_{1} \textit{ if and only if } f(x) \in L_{2}.\]
The logarithmic space reduction is used in the definition of the complete languages for the classes $L$ and $NL$ \cite{Pap03}. A Boolean formula is in 2-conjunctive normal form, or $2CNF$, if it is in $CNF$ and each clause has exactly two distinct literals. There is a problem called $2SAT$, where we asked whether a given Boolean formula $\phi$ in $2CNF$ is satisfiable. $2SAT$ is complete for $NL$ \cite{Pap03}. Another special case is the class of problems where each clause contains $XOR$ (i.e. exclusive or) rather than (plain) $OR$ operators. This is in $P$, since an $\textit{XOR SAT}$ formula can also be viewed as a system of linear equations mod $2$, and can be solved in cubic time by Gaussian elimination \cite{MM11}. We denote the $XOR$ function as $\oplus$. The $\textit{XOR 2SAT}$ problem will be equivalent to $\textit{XOR SAT}$, but the clauses in the formula have at most two distinct literals \cite{AR00}. $\textit{XOR 2SAT}$ is in $L$ \cite{AR00}, \cite{RM08}.

@@

\begin{definition}
A language $L_{1}$ is in $NL$ if there exists a deterministic logarithmic space Turing machine $M$ with an additional special read-once input tape polynomial $p: \mathbb{N} \rightarrow \mathbb{N}$ such that for every $x \in \{0, 1\}^{*}$:
\[x \in L_{1} \Leftrightarrow \exists \textit{ appropriated } u \in \{0, 1\}^{p(|x|)} \textit{ such that } M(x, u) = ``yes" \]
where by $M(x, u)$ we denote the computation of $M$ where $x$ is placed on its input tape and the certificate $u$ is placed on its special read-once tape, and $M$ uses at most $O(\log |x|)$ space on its read/write tapes for every input $x$ where $|\ldots|$ is the bit-length function \cite{AB09}. $M$ is called a logarithmic space verifier \cite{AB09}.
\end{definition}

An important complexity class is $\textit{coNP--complete}$ \cite{GJ79}. A language $L_{1} \subseteq \{0, 1\}^{*}$ is $\textit{coNP--complete}$ if:

\begin{itemize}
\item $L_{1} \in coNP$, and
\item $L' \leq_{p} L_{1}$ for every $L' \in coNP$.
\end{itemize}

If $L_{1}$ is a language such that $L' \leq_{p} L_{1}$ for some $L' \in \textit{coNP--complete}$, then $L_{1}$ is $\textit{coNP--hard}$ \cite{CLRS01}. Moreover, if $L_{1} \in coNP$, then $L_{1} \in \textit{coNP--complete}$ \cite{CLRS01}. A principal $\textit{coNP--complete}$ problem is $UNSAT$ \cite{GJ79}. A Boolean formula without any satisfying truth assignment is unsatisfiable. The problem $UNSAT$ asks whether a given Boolean formula is unsatisfiable \cite{GJ79}.

$coNL$ is the complexity class containing the languages such that their complements belong to $NL$ \cite{Pap03}. We can give a disqualification-based definition for $coNL$ \cite{AB09}. The disqualification-based definition of $coNL$ assumes that a logarithmic space Turing machine has another separated read-only tape, that is the same kind of special tape called $``$read-once$"$ that we use in the certificate-based definition for $NL$ \cite{AB09}. Besides, in the disqualification-based definition of $coNL$, we assume the disqualification string is appropriated for the instance \cite{Pap03}.

\begin{definition}
A language $L_{1}$ is in $coNL$ if there exists a deterministic logarithmic space Turing machine $M$ with an additional special read-once input tape polynomial $p: \mathbb{N} \rightarrow \mathbb{N}$ such that for every $x \in \{0, 1\}^{*}$:
\[x \in L_{1} \Leftrightarrow \forall \textit{ appropriated } u \in \{0, 1\}^{p(|x|)} \textit{ then } M(x, u) = ``yes" \]
where by $M(x, u)$ we denote the computation of $M$ where $x$ is placed on its input tape and the disqualification $u$ is placed on its special read-once tape, and $M$ uses at most $O(\log |x|)$ space on its read/write tapes for every input $x$ where $|\ldots|$ is the bit-length function. $M$ is called a logarithmic space disqualifier.
\end{definition}

For example, there is a well-known $coNL$ problem that states: Given a directed graph $G = (V, E)$ and two nodes $s, t \in V$, is there no possible path from $s$ to $t$? In that problem, an appropriated disqualification $u$ is a sequence of nodes contained in $V$ when $s$ is the first node and $t$ is the last one such that this sequence of nodes is not a path: There is at least a consecutive pair of nodes in the sequence where they are not connected by an edge.

From the early days of automata and complexity theory,  two  different  models  of  Turing  machines  are  considered, the offline and online machines \cite{KU15}. Each model has a read-only input tape and some work tapes \cite{KU15}. The offline machines may read their input two-way while the online machines are not allowed to move the input head to the left \cite{KU15}. In the terminology of the (generalized) Turing machine models are called two-way and one-way Turing machines, respectively \cite{KU15}.

Hartmanis and Mahaney have investigated the classes $1L$ and $1NL$ of languages recognizable by deterministic one-way logarithmic space Turing machine and nondeterministic one-way logarithmic space Turing machine, respectively \cite{HM81}. They have shown that $1L \neq 1NL$ (by looking at a uniform variant of the string non-equality problem from communication complexity theory) and have defined a natural complete problem for $1NL$ under deterministic one-way logarithmic space reductions \cite{HM81}. Furthermore, they have proven that $1NL \subseteq L$ if and only if $L=NL$ \cite{HM81}.

@@

\begin{hypothesis}
\label{hypothesis2}
Given a nonempty language $L_{1} \in 1NL$, there is a language $L_{2}$ in $\textit{coNP--complete}$ with a deterministic Turing machine $M$, where:
\[L_{2} = \{w: M(w, u) = y, \forall \textit{ appropriated } u \textit{ such that } y \in L_{1}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$. In this way, there is a $\textit{coNP--complete}$ language defined by a logarithmic space disqualifier $M$ such that when the input is an element of the language with any of its appropriated disqualification, then $M$ always outputs a string which belongs to a single language in $1NL$.
\end{hypothesis}

\begin{theorem}
\label{pos-implication}
If the Hypothesis \ref{hypothesis2} is true, therefore when $L = NL$, then $P = NP$.
\end{theorem}

\begin{proof}
We can accept the elements of the language $L_{1} \in 1NL$ by a nondeterministic one-way logarithmic space Turing machine $M'$. In this way, there is a nondeterministic logarithmic space Turing machine $M''(w, u) = M'(M(w, u))$ which will accept when $w \in L_{2}$ for all the appropriated disqualification $u$, where $u$ is placed on the special read-once tape of $M''$. The reason is because we can simulate the output string of $M(w, u)$ within a read-once tape and thus, we can compute in a nondeterministic logarithmic space the logarithmic space composition using the same techniques of the logarithmic space composition reduction, but without any reset of the computation \cite{Pap03}. Certainly, we do not need to reset the computation of $M(w, u)$ for the reading at once of a symbol in the output string of $M(w, u)$ by the nondeterministic one-way logarithmic space Turing machine $M'$. Consequently, $M''$ can be converted into a logarithmic space disqualifier for the language $L_{2}$ just assuming that $L = NL$, because of the nondeterministic logarithmic space Turing machine $M''$ could be simulated by a deterministic logarithmic space Turing machine. Therefore, $L_{2}$ is in $coNL$ and thus, $L_{2} \in P$ due to $coNL \subseteq P$ \cite{Pap03}. If any single $\textit{coNP--complete}$ problem can be solved in polynomial time, then $P = NP$ \cite{Pap03}. Since $L_{2} \in P$ and $L_{2} \in \textit{coNP--complete}$, then we obtain the complexity class $P$ is equal to $NP$ under the assumption that $L = NL$.
\end{proof}

@@

We show a previous known $\textit{coNP--complete}$ problem:

\begin{definition}
$\textbf{3UNSAT}$

@@

QUESTION: Is $\phi$ unsatisfiable?

REMARKS: $3UNSAT \in \textit{coNP--complete}$ \cite{GJ79}.
\end{definition}

@@

\begin{definition}
$\textbf{SUM ZERO}$

INSTANCE: A collection of integers $C$ such that $0 \notin C$ and every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$ (we do not take into account the symbol minus in counting the bit-length of the negative integers).

QUESTION: Are there two elements $a, b \in C$, such that $a + b = 0$?

REMARKS: We denote this problem as $\textit{SUM--ZERO}$.
\end{definition}

\begin{theorem}
\label{1nl}
$\textit{SUM--ZERO} \in 1NL$.
\end{theorem}

\begin{proof}
Given a collection of integers $C$, we can read its elements from left to right, verify that every element is not equal to $0$, check that every element in $C$ has the same bit-length and count the amount of elements in $C$ to finally multiply it by $3$ and compare its bit-length with the single bit-length from the elements in $C$. In addition, we can nondeterministically pick two elements $a$ and $b$ from $C$ and accept in case of $a + b = 0$ otherwise we reject. We can make all this computation in a nondeterministic one-way using logarithmic space. Certainly, the calculation and store of the bit-length of the elements in $C$ could be done in logarithmic space since this is a unique value. On the one hand, we can count and store the number of elements that we read from the input and multiply it by $3$ to finally compare its bit-length with the stored unique bit-length from the elements of the collection, since the cardinality of $C$ multiplied by $3$ could be stored in a binary number of bit-length that is logarithmic in relation to the encoded length of $C$. On the other hand, the two elements $a$ and $b$ that we pick from $C$ have a logarithmic space in relation to the encoded length of $C$, because of every integer in $C$ has the same bit-length of the number that represents the cardinality of $C$ multiplied by $3$. Indeed, we never need to read to the left on the input for the acceptance of the elements in $\textit{SUM--ZERO}$ in a nondeterministic logarithmic space.
\end{proof}

\begin{theorem}
\label{demonstration}
There is a deterministic Turing machine $M$, where:
\[3UNSAT = \{w: M(w, u) = y, \forall \textit{ appropriated } u \textit{ such that } y \in \textit{SUM--ZERO}\}\]
when $M$ runs in logarithmic space in the length of $w$, $u$ is placed on the special read-once tape of $M$, and $u$ is polynomially bounded by $w$.
\end{theorem}

\begin{proof}
Given a Boolean formula $\phi$ in $3CNF$ with $n$ variables and $m$ clauses, we can create a disqualification array $A$ which contains $m$ positive integers between $1$ and $3$ which represents the literals of the clauses in $\phi$ which appear from left to right. We read at once the elements of the array $A$ and we reject whether this is not an appropriated disqualification: That is when the array $A$ does not contain exactly $m$ elements, or the array $A$ contains a number that is not between $1$ and $3$. While we read the elements of the array $A$, we select from the clauses $\phi$ the literals such that these ones occupy the position that represents the number between $1$ and $3$, that is the first, second or third place within the clause from left to right. In this way, we output the selected literals that are represented by a positive or negative (in case of a negated variable) integer just creating another instance $C$ for $\textit{SUM--ZERO}$ where the collection $C$ contains those integers which are the selected literals for each clause in $\phi$. Therefore, we obtain that all the appropriated array $A$ would be valid according to the Theorem \ref{demonstration} when:
\[\phi \in 3UNSAT \Leftrightarrow (\forall \textit{ appropriated array } A \textit{ such that } C \in \textit{SUM--ZERO})\]
since we assume the positive and negated literals of some variable in the input $\phi$ correspond to a positive integer and its negative value, respectively. Furthermore, we can make this disqualification in logarithmic space such that the array $A$ is placed on the special read-once tape, because we read at once the elements in the array $A$. Hence, we only need to iterate from the elements of the array $A$ to verify whether the array is an appropriated disqualification and pick the $m$ literals from the Boolean formula $\phi$ when we write the final integers that represent these literals to the output. This logarithmic space disqualification will be the Algorithm \ref{algorithm2}. We assume whether a value does not exist in the array $A$ into the cell of some position $i$ when $A[i] = \textit{undefined}$. In addition, we reject immediately when the following comparisons:
\[A[i] < 1 \vee A[i] > 3\]
hold at least into one single binary digit. Note, that every possible literal in $\phi$ could have a representation by an integer between $-3 \times m$ and $3 \times m$ with the exception of $0$, where $m$ is the cardinality of the collection $C$. In this way, we guarantee the output collection $C$ is an appropriated instance of $\textit{SUM--ZERO}$ just filling with zeroes to the left the elements with bit-length lesser than $|3 \times m|$ where $|\ldots|$ is the bit-length function.

\begin{algorithm}
\caption{Logarithmic space disqualifier}\label{algorithm2}
\begin{algorithmic}[1]
\Comment{A valid instance for $3UNSAT$ with its disqualification}
\Procedure{$\textit{DISQUALIFIER}$}{$\phi, A$}
\Comment{Initialize an index}
\State $j \gets 0$
\Comment{$m$ is the number of clauses in $\phi$}
\Comment{Iterate for the elements of the disqualification array $A$}
\For{$i$}{$1$}{$m + 1$}
\If{$i = m+1$}
\Comment{There exists an $m+1$ element in the array}
\If{$A[i] \neq \textit{undefined}$}
\Comment{Reject the disqualification}
\State \textbf{return} $``no"$
\EndIf
\Comment{Break the $\textbf{for}$ loop}
\State \textbf{break}
\ElsIf{$A[i] = \textit{undefined} \vee A[i] < 1 \vee A[i] > 3$}
\Comment{Reject the disqualification}
\State \textbf{return} $``no"$
\Else
\State $j \gets A[i]$
\EndIf
\Comment{From the indexed $i^{th}$ clause $c_{i} = (x_{j} \vee y_{k} \vee z_{r})$ in $\phi$}
\Comment{Where $x$, $y$ and $z$ are literals with local indexes $\{j, k, r\} = \{1,2,3\}$ in $c_{i}$}
\Comment{Output the integer representation of the $j^{th}$ literal, that is $n(x_{j})$}
\Comment{Filled with zeroes to the left until a total of $|3 \times m|$ bits including the literal}
\Comment{But, the bit-length of the symbol minus is ignored in filling the negated literals}
\State \textbf{output} $``\ , \ n(x_{j})"$
\EndFor
\EndProcedure
\end{algorithmic}
\end{algorithm}
\end{proof}

\begin{theorem}
\label{result2}
The Hypothesis \ref{hypothesis2} is true.
\end{theorem}

\begin{proof}
This is a consequence of Theorems \ref{1nl} and \ref{demonstration}.
\end{proof}

\begin{theorem}
\label{equal-NP}
If $L = NL$ then $P = NP$.
\end{theorem}

\begin{proof}
This is a direct consequence of Theorems \ref{pos-implication} and \ref{result2}.
\end{proof}

\subsection{L versus NL}

A directed acyclic graph $G = (V, E)$ is topologically sorted when for any pair of edges $(a, b)$ and $(b, c)$ in $G$, then the edge $(a, b)$ is listed before $(b, c)$ \cite{HM81}.

We show a previous known $\textit{NL--complete}$ problem:

\begin{definition}
$\textbf{TAGAP}$

INSTANCE: Given a directed acyclic graph $G = (V, E)$ that is topologically sorted and two nodes $s, t \in V$.

QUESTION: Is there a path from $s$ to $t$?

REMARKS: $TAGAP \in \textit{NL--complete}$ \cite{HM81}.
\end{definition}

\begin{definition}
An instance $\phi$ of $\textit{XOR 2SAT}$ is topologically sorted when for any pair of clauses $(a, b)$ and $(b, c)$ in $\phi$, then the clause $(a, b)$ is listed before $(b, c)$.
\end{definition}

\begin{definition}
$\textbf{TAGAP 2SAT}$

INSTANCE: Given an instance $\phi$ of $\textit{XOR 2SAT}$ that is topologically sorted.

QUESTION: Is there a truth assignment, such that each clause of one literal is satisfied and each clause of two literals has not a true and false evaluated literals at the same time?
\end{definition}

\begin{theorem}
$\textit{TAGAP 2SAT} \in L$.
\end{theorem}
